Enhancing Student Engagement via Reduction of Frustration with Programming Assignments using Machine Learning

### 2017-06-12 paper.tex
Repositioned URLs

\subsubsection{Capturing the Keystroke and Mouse Data} 
While a student is trying
to solve an exercise, a script coded in JavaScript is running in the background,
which captures every keystroke, mouse movement and mouse button press. Each
capture of these events records a time-stamp in milliseconds (using the method
getTime() of JavaScript's built-in class Date) that describes when the event
occurred. If the event is a keystroke, the script captures what key was
specifically pressed, and what type of event occurred, it can be either a key-
down or a key-up event. If it is an event related to a mouse button press, the
key code of that button is recorded, as well as the type of event occurred again
key-down or key-up. Finally, if the event was a mouse movement, the mouse
coordinates inside of the web browser are recorded. The script monitors the
mouse position every 100 milliseconds, and only if the position has changed, it
records the new position. Each time a learner tries to evaluate a program, all
the data generated is sent to the server along with the code. When the result of
the execution is returned, all records are cleared and the process starts again.
There is no problem if the user leaves for a long period of time, because no
event will be triggered. If a user copies and then pastes the code from another
source, this will be recorded. There is a limitation, only the browser-editor
must be used; this could be a problem for more advanced programmers needing
specialized editors.  On the other hand a browser-based editor with the
corresponding remote execution, does not require the installation of
interpreters or compilers in learner’s computer. The code could even be written
in a mobile device or any web-enabled device. Programming exercises are evaluated using unit
tests; the results of the evaluation are shown to users. If all tests the
program is considered to be correct. The source code for the Protoboard web
based learning environment including the KD and MD functions are open source and
available as Github repositories. %at http://--------.--/----- also the code for the
sandbox is in \url{https://github.com/mariosky/sandbox}.

>>>>

\subsubsection{Capturing the Keystroke and Mouse Data} 
While a student is trying
to solve an exercise, a script coded in JavaScript is running in the background,
which captures every keystroke, mouse movement and mouse button press. Each
capture of these events records a time-stamp in milliseconds (using the method
getTime() of JavaScript's built-in class Date) that describes when the event
occurred. If the event is a keystroke, the script captures what key was
specifically pressed, and what type of event occurred, it can be either a key-
down or a key-up event. If it is an event related to a mouse button press, the
key code of that button is recorded, as well as the type of event occurred again
key-down or key-up. Finally, if the event was a mouse movement, the mouse
coordinates inside of the web browser are recorded. The script monitors the
mouse position every 100 milliseconds, and only if the position has changed, it
records the new position. Each time a learner tries to evaluate a program, all
the data generated is sent to the server along with the code. When the result of
the execution is returned, all records are cleared and the process starts again.
There is no problem if the user leaves for a long period of time, because no
event will be triggered. If a user copies and then pastes the code from another
source, this will be recorded. There is a limitation, only the browser-editor
must be used; this could be a problem for more advanced programmers needing
specialized editors.  On the other hand a browser-based editor with the
corresponding remote execution, does not require the installation of
interpreters or compilers in learner’s computer. The code could even be written
in a mobile device or any web-enabled device. Programming exercises are evaluated using unit
tests; the results of the evaluation are shown to users. If all tests the
program is considered to be correct. The source code for the Protoboard web
based learning environment including the KD and MD functions are open source and
available as Github repositories at \url{https://github.com/mariosky/sandbox}; the code for the
sandbox is also in \url{https://github.com/mariosky/sandbox}.
